A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.

### 2021-12-22 inst/manuscript/supporting.Rmd
minor updates before submission

---
title: A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.
author:
  - name: Michael Dumelle
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    affiliation: STLAW
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)"
journal: "Methods in Ecology and Evolution"
date: "`r Sys.Date()`"
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
preamble: >
  \usepackage{bm}
  \usepackage{bbm}
  \usepackage{color}
  \DeclareMathOperator{\var}{{var}}
  \DeclareMathOperator{\cov}{{cov}}
  \renewenvironment{abstract}{}{}
output: rticles::elsevier_article
---

# Simulation Study Tables {#sec:simtabs}

@@

Next we present tables summarizing mean estimation bias (design-based) or mean prediction bias (model-based), mean standard errors, root-mean-squared error (design-based) or root-mean-squared-prediction error (model-based), and 95% confidence interval coverage (design-based) or 95% prediction interval coverage (model-based) for all 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  PDE = psill_ratio,
                  n = n,
                  Bias = mpbias,
                  `rMS(P)E` = rmspe,
                  MStdE = mse,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-Design",
       Approach == "Design IRS" ~ "IRS-Design",
       Approach == "Model GRTS" ~ "GRTS-Model",
       Approach == "Model IRS" ~ "IRS-Model"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Lognormal"
     ),
     across(c(PDE, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = paste0("Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\\% interval coverage (Coverage) in simulation scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("llllrrrrrr")
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```

>>>>

---
title: A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.
author:
  - name: Michael Dumelle
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    affiliation: STLAW
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)"
journal: "Methods in Ecology and Evolution"
date: "`r Sys.Date()`"
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
preamble: >
  \usepackage{bm}
  \usepackage{bbm}
  \usepackage{color}
  \DeclareMathOperator{\var}{{var}}
  \DeclareMathOperator{\cov}{{cov}}
  \renewenvironment{abstract}{}{}
output: rticles::elsevier_article
---

# Simulation study tables {#sec:simtabs}

@@

Next we present tables summarizing mean estimation bias (design-based) or mean prediction bias (model-based), root-mean-squared error (design-based) or root-mean-squared-prediction error (model-based), mean standard errors, and 95% confidence interval coverage (design-based) or 95% prediction interval coverage (model-based) for all 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  PDE = psill_ratio,
                  n = n,
                  Bias = mpbias,
                  `rMS(P)E` = rmspe,
                  MStdE = mse,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-Design",
       Approach == "Design IRS" ~ "IRS-Design",
       Approach == "Model GRTS" ~ "GRTS-Model",
       Approach == "Model IRS" ~ "IRS-Model"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Lognormal"
     ),
     across(c(PDE, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = paste0("Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\\% interval coverage (Coverage) in simulation scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("llllrrrrrr")
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```

### 2021-12-22 inst/manuscript/supporting.tex
minor updates before submission

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supporting Information.}
    \author[USEPA]{Michael Dumelle\corref{1}}

@@

\hypertarget{sec:simtabs}{%
\section{Simulation Study Tables}\label{sec:simtabs}}

@@

Next we present tables summarizing mean estimation bias (design-based)
or mean prediction bias (model-based), mean standard errors,
root-mean-squared error (design-based) or root-mean-squared-prediction
error (model-based), and 95\% confidence interval coverage
(design-based) or 95\% prediction interval coverage (model-based) for
all 36 simulation scenarios.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supporting information.}
    \author[USEPA]{Michael Dumelle\corref{1}}

@@

\hypertarget{sec:simtabs}{%
\section{Simulation study tables}\label{sec:simtabs}}

@@

Next we present tables summarizing mean estimation bias (design-based)
or mean prediction bias (model-based), root-mean-squared error
(design-based) or root-mean-squared-prediction error (model-based), mean
standard errors, and 95\% confidence interval coverage (design-based) or
95\% prediction interval coverage (model-based) for all 36 simulation
scenarios.
